%! TEX program = xelatex
\documentclass[11pt,a4paper,oneside]{report}

\usepackage{parskip}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{longtable,booktabs,array}

\usepackage{titlesec}
\titleformat{\chapter}[display]
{\sffamily\bfseries\huge}
{\Large \chaptertitlename\ \thechapter}
{2ex}
{\titlerule
    \vspace{1ex}%
    \filright\MakeUppercase}
[\vspace{1ex}%
    \titlerule]
\titleformat{\section}{\normalfont\sffamily\Large\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}{\normalfont\sffamily\large\bfseries}{\thesubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\sffamily\normalsize\bfseries}{\thesubsubsection}{1em}{}

\usepackage[style=numeric-comp, url=false]{biblatex}
\addbibresource{bibfile.bib}

\usepackage{fontspec}
\setmainfont{TeX Gyre Termes}
\setsansfont{TeX Gyre Termes}

\usepackage{upquote}
\usepackage[allcolors=blue,colorlinks=true]{hyperref}
\usepackage{xurl}
\usepackage{microtype}
\usepackage{bookmark}
\usepackage{calc}
\usepackage{etoolbox}

\urlstyle{same}

\usepackage{pifont}  % for the checkmark/crossmark
\usepackage{graphicx}

\usepackage{algorithmic}
\usepackage[ruled]{algorithm2e}

\usepackage{xspace}
\newcommand{\fedcampus}{\textsc{FedCampus}\xspace}
\newcommand{\fedkit}{\textsc{FedKit}\xspace}

\begin{document}


% Author name (capitalized in its regular way)
\newcommand{\authorname}{Steven Hé (Sīchàng)}

% Title (cannot exceed three lines)
\newcommand{\thetitle}{Integrating Federated Learning for \fedcampus,
    A Privacy-Preserving Data Platform for Smart Campuses
}

% Date of submission with normal capitalization. Use the format January 29, 2022.
\newcommand{\submissiondate}{March 7, 2024}

% Mentor: First Name Last Name (normal capitalization)
\newcommand{\mentor}{Bing Luo}

% Academic Unit (no abbreviations)
\newcommand{\academicunit}{Division of Natural and Applied Sciences}

\vspace*{\bigskipamount}

\begin{center}
    {\sffamily\LARGE\bfseries\MakeUppercase\thetitle\par}

    \bigskip

    by

    \bigskip

    {\Large \authorname}

    \bigskip

    Mentor: \mentor, \academicunit\\[12pt]
    Signature Work Product, in partial fulfillment of the \\
    Duke Kunshan University Undergraduate Degree Program

    \bigskip

    \emph{\submissiondate}

    \bigskip

    Signature Work Program \\
    Duke Kunshan University

\end{center}

\vfill

\emph{\textbf{Abstract.}}
\fedcampus endeavors to establish a privacy-preserving data platform for
university campuses,
extracting valuable insights while preserving participants' privacy.
This initial phase focuses on accessing personal health data on participants'
smartphones and executing cross-platform federated learning. Federated learning,
a privacy-preserving machine learning technique,
enables model training across multiple edge devices without centralizing raw
data. However,
challenges brought by \fedcampus' advanced requirements for real-world federated
learning on smartphones, including cross-platform support,
dependency on application updates, and interdisciplinary collaboration,
were not addressed by existing federated learning systems. \fedkit,
our innovative software development kits,
address these challenges through a machine learning model pipeline and machine
learning operations support.
Experiments were conducted in both lab-based settings and on The \fedcampus
Application, a smartphone application deployed among students, staff,
and faculty at Duke Kunshan University.
Results underscored the effectiveness of \fedkit and the feasibility of
\fedcampus' overall approach,
paving the way for future advancements towards a comprehensive data platform.

\vspace{4\bigskipamount}

\end{document}
